---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
## so jittered figs don't always appear to be changed
set.seed(1)
```

# gapminder

<!-- badges: start -->
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.594018.svg)](https://doi.org/10.5281/zenodo.594018)
[![CRAN status](https://www.r-pkg.org/badges/version/gapminder)](https://CRAN.R-project.org/package=gapminder)
![](http://cranlogs.r-pkg.org/badges/grand-total/gapminder)
[![R-CMD-check](https://github.com/jennybc/gapminder/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jennybc/gapminder/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This repo is a data package with an excerpt from the [Gapminder](https://www.gapminder.org/data/) data.
The main object in this package is the `gapminder` data frame or "tibble".
There are other goodies, such as the data in tab delimited form, a larger unfiltered dataset, premade color schemes for the countries and continents, and ISO 3166-1 country codes.
The primary use case is for teaching and writing examples.

## Installation

Install `gapminder` from CRAN:

```{r eval = FALSE}
install.packages("gapminder")
```

## Quick look

Here we do a bit of data aggregation and plotting with the `gapminder` data:

```{r test-drive, message = FALSE, warning = FALSE, out.width = "60%"}
library(gapminder)
library(dplyr)
library(ggplot2)

aggregate(lifeExp ~ continent, gapminder, median)

gapminder %>%
  filter(year == 2007) %>%
  group_by(continent) %>%
  summarise(lifeExp = median(lifeExp))

ggplot(gapminder, aes(x = continent, y = lifeExp)) +
  geom_boxplot(outlier.colour = "hotpink") +
  geom_jitter(position = position_jitter(width = 0.1, height = 0), alpha = 1 / 4)
```

For more, see the [Get started](https://jennybc.github.io/gapminder/articles/gapminder.html) vignette.